Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2015-01-26 Paper/ms.tex
ellipticity --> eccentricity
New references suggested by the referee

It is now well known that RV datasets can contain periodic signals
resulting from stellar activity rather than planets \citep{2014Sci...345..440R}.
Therefore, it is important to develop models which attempt to distinguish
stellar activity signals from Keplerian planet signals based on the shape of
the oscillations and/or additional data constraining the periods of any
stellar activity signals. We do not address this important challenge in the
present paper. Rather, we consider the problem of inferring the number $N$ of
Keplerian signals in an RV dataset in a computationally efficient way.

@@

\section{Orbit Look-Up Table}\label{sec:orbits}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape $m(t)$ of the variations is needed in order to evaluate the likelihood
function for any proposed setting of the parameters.
To save time, we pre-computed the properties of orbits as a function of
ellipticity. We also made the standard assumption that the planets do not
interact, so the expected signal due to several planets is the sum of the
contributions of each planet.

@@

@@

\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
submitted. ArXiv: 1411.3921

@@

>>>>

It is well known that RV datasets can contain periodic signals
resulting from stellar activity rather than planets,
which can affect the conclusions we draw about
exoplanet systems \citep[e.g.][]{2001A&A...379..279Q, 2007A&A...474..293B, 2014Sci...345..440R}.
Therefore, it is important to develop models which attempt to distinguish
stellar activity signals from Keplerian planet signals based on the shape of
the oscillations and/or additional data constraining the periods of any
stellar activity signals. We do not address this important challenge in the
present paper. Rather, we consider the problem of inferring the number $N$ of
Keplerian signals in an RV dataset in a computationally efficient way, under
the simplifying assumption that only Keplerian signals are present in the data.

@@

\section{Orbit Look-Up Table}\label{sec:orbits}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape $m(t)$ of the variations is needed in order to evaluate the likelihood
function for any proposed setting of the parameters.
To save time, we pre-computed the properties of orbits as a function of
eccentricity. We also made the standard assumption that the planets do not
interact, so the expected signal due to several planets is the sum of the
contributions of each planet.

@@

\bibitem[Bonfils et 
al.(2007)]{2007A&A...474..293B} Bonfils, X., Mayor, M., Delfosse, X., et al.\ 2007, A\&A, 474, 293

@@

\bibitem[\protect\citeauthoryear{Brewer}{2014}]{rjobject} Brewer, B. J., 2014,
ArXiv: 1411.3921

@@

\bibitem[Queloz et 
al.(2001)]{2001A&A...379..279Q} Queloz, D., Henry, G.~W., Sivan, J.~P., et al.\ 2001, A\&A, 379, 279
